---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ggArtsyR

<!-- badges: start -->
<!-- badges: end -->

List of things to include in README from R Packages book, for our reference:

1. A paragraph that describes the high-level purpose of the package.

2. An example that shows how to use the package to solve a simple problem.

3. Installation instructions, giving code that can be copied and pasted into R.

4. An overview that describes the main components of the package. For more complex packages, this will point to vignettes for more details.

At this point in its development, the ggArtsyR package works with `ggplot2()` to add an additional color palette to the user’s repertoire. This is the goghColors dataset, which contains the RGB codes of colors picked from Van Gogh paintings. It also has a function that work alongside `ggplot2()` to create more interesting data visualizations and add contextual information to the user’s plots. This main function is `RectangleFiller()`, which divides data visualizations into colored quadrants, improving the readability of graphs. 


```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub.
